Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-07-09 Article_B8/Article_B8.Rmd
Commit 2024-07-09 22:18

```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023."}
knitr::include_graphics("../images/groups-1.png")
```

>>>>

```{r ceg-duration-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023. The histogram was splited in two plots with differnt y-axis limits for better readability."}
# knitr::include_graphics("../images/groups-1.png")
knitr::include_graphics("../images/groups-7.png")
```

### 2024-07-09 Article_B8/Article_B8_plain.tex
Commit 2024-07-09 22:18

{\centering \includegraphics[width=1\linewidth]{../images/groups-1}

@@

\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023.}\label{fig:ceg-duration-distribution}
\end{figure}

>>>>

{\centering \includegraphics[width=1\linewidth]{../images/groups-7}

@@

\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023. The histogram was splited in two plots with differnt y-axis limits for better readability.}\label{fig:ceg-duration-distribution}
\end{figure}
